---
title: "Post Operative Patient Admission ML Support Vector Machines"
author: "Rex Manglicmot"
output: 
  github_document: 
    toc: yes
---

## Status: Continuing Working Document

## Introduction

The attributes are as follows:

1. L-CORE (patient's internal temperature in C):
high (> 37), mid (>= 36 and <= 37), low (< 36)

2. L-SURF (patient's surface temperature in C):
high (> 36.5), mid (>= 36.5 and <= 35), low (< 35)

3. L-O2 (oxygen saturation in %):
excellent (>= 98), good (>= 90 and < 98),
fair (>= 80 and < 90), poor (< 80)

4. L-BP (last measurement of blood pressure):
high (> 130/90), mid (<= 130/90 and >= 90/70), low (< 90/70)

5. SURF-STBL (stability of patient's surface temperature):
stable, mod-stable, unstable
6. CORE-STBL (stability of patient's core temperature)
stable, mod-stable, unstable

7. BP-STBL (stability of patient's blood pressure)
stable, mod-stable, unstable

8. COMFORT (patient's perceived comfort at discharge, measured as
an integer between 0 and 20)

9. decision ADM-DECS (discharge decision):
I (patient sent to Intensive Care Unit),
S (patient prepared to go home),
A (patient sent to general hospital floor)

## Loading the Libraries
```{r, message=FALSE}
library(tidyverse)

```


## Loading the Data
```{r}
#create object to load files from the web
url <- 'https://archive.ics.uci.edu/ml/machine-learning-databases/postoperative-patient-data/post-operative.data'

#load the data
data <- read.csv(url, header=TRUE)
```

## Cleaning the Data
OH BOY, we got some cleaning to do!
```{r}
#view the first few rows of the data
head(data)
dim(data)
```
Calling the dim function, we have 89 rows and 9 columns. According to the UCI website, there should be 90 rows. It would seem that the column names are actually an observation and adding that back to the dataframe would make the dataset whole. Let's create a new row.

Also, because the original column names are missing from the dataset, we would have to assume that the column names go in the order in which it was presented on the UCI website. As such, I will rename the columns accordingly. 

```{r}
#add another row the the dataset filled with values from the column
#row will added to the bottom of the dataset
data[nrow(data) +1,] <- c('mid', 'low', 'excellent', 'mid', 'stable', 'stable', 'stable', '15', 'A')

#check the last row
tail(data, 1)

#change column names and make them shorter
colnames(data) <- c('itemp', 'stemp', 'osat', 'bp', 'stabitemp', 'stabstep', 'stabosat', 'comf', 'deci')

#check if it worked
names(data)
```

```{r}
#change to appropiate class

```


## Support Vector Machines


## Limitations


## Conclusions

## Inspiration for this project 
